Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-09-22 supplement.tex
minor change to last commit
author list on supplement

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

\begin{figure}
  \toprule \begin{minipage}[c]{\textwidth}
    \begin{align*}
      \probability[p|\mathcal{D},\theta]& = P_{\mathcal{D},\theta} (p|\tau,\varnothing )\text{, where $p:\tau$}\\
      P_{\mathcal{D},\theta} (\lambda z.p|\alpha\to\beta,\mathcal{E})& =
      P_{\mathcal{D},\theta}(p|\beta,[\tau\mapsto\alpha]\mathcal{E})\text{, where $\tau$ a fresh type variable}\\
      P_{\mathcal{D},\theta}(e|\tau,\mathcal{E})& = \underbrace{\sum_{f,xs\in \text{parse}(e)} P'_{\mathcal{D},\theta}(f,xs|\tau,\mathcal{E})}_{\text{Marginalizing out how $\mathcal{D}$ produced $e$}}\text{, when $e$ not a $\lambda$-abstraction}\\
      \\
      P'_{\mathcal{D},\theta}(f,xs|\tau,\mathcal{E})& = \underbrace{\sum_{f':\tau_1\to\tau_2\to\cdots\to\tau\in \mathcal{D}}\frac{\theta_f}{Z_{\tau,\mathcal{D},\theta,\mathcal{E}}}
        \indicator[\text{match}(f',f)\not=\bot]}_{\text{Marginalize over which fragment produced $f,xs$}}\times\\&\prod_{n=1}^{|xs|}P_{\mathcal{D},\theta}(x_n|\tau_n,\mathcal{E})\prod_{e,\tau'\in \text{match}(f',f)}P_{\mathcal{D},\theta}(e|\tau',\mathcal{E})\\
      \\
      \text{match}(\lambda z.b,\lambda z.b')& = \text{match}(b,b')\\
      \text{match}(f\;x,f'\;x')& = \text{match}(f,f')\cup\text{match}(x,x')\\
      \text{match}(p,p)& = \varnothing \text{, $p$ a primitive or variable bound in fragment}\\
      \text{match}(v,p)& = \left\{v\mapsto p   \right\} \text{, $v$ a variable free in fragment}\\
      \text{match}(e,e')& = \bot\text{, otherwise.}
      \\
      \\
      Z_{\tau,\mathcal{D},\theta,\mathcal{E}}& = \underbrace{\sum_{f:\tau_1\to\tau_2\to\cdots\to\tau\in \mathcal{D}\cup\mathcal{E}}\theta_f}_{\text{Normalizing constant for type $\tau$}}\\\\
      \text{parse}(f\;x)& = \left\{f',xs+[x] \;|\; f',xs\in \text{parse}(f) \right\}\cup\left\{f\;x \right\}\\
      \text{parse}(e)& = \left\{e,[] \right\} \text{, $e$ not an application}
    \end{align*}
  \end{minipage}
  \bottomrule
  \caption{Procedure for calculating likelihood of a program after a new fragment has been added to the DSL. For simplicity we omit typing context and reuse type variables to indicate unification, as is commonly done in e.g. Prolog.}\label{match}
  \end{figure}

>>>>

\author{
  Kevin Ellis\\MIT\\\texttt{ellisk@mit.edu}\And Lucas Morales\\MIT\And Mathias Sabl\'e-Meyer\\ENS Paris-Saclay
  \AND
  Armando Solar-Lezama\\MIT\And Joshua B. Tenenbaum\\MIT
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

\begin{figure}
  \toprule \begin{minipage}[c]{\textwidth}
    \begin{align*}
      \probability[p|\mathcal{D},\theta]& = P_{\mathcal{D},\theta} (p|\tau,\varnothing )\text{, where $p:\tau$}\\
      P_{\mathcal{D},\theta} (\lambda z.p|\alpha\to\beta,\mathcal{E})& =
      P_{\mathcal{D},\theta}(p|\beta,[\tau\mapsto\alpha]\mathcal{E})\text{, where $\tau$ a fresh type variable}\\
      P_{\mathcal{D},\theta}(e|\tau,\mathcal{E})& = \underbrace{\sum_{f,xs\in \text{parse}(e)} P'_{\mathcal{D},\theta}(f,xs|\tau,\mathcal{E})}_{\text{Marginalizing out how $\mathcal{D}$ produced $e$}}\text{, when $e$ not a $\lambda$-abstraction}\\
      \\
      P'_{\mathcal{D},\theta}(f,xs|\tau,\mathcal{E})& = \underbrace{\sum_{f':\tau_1\to\tau_2\to\cdots\to\tau\in \mathcal{D}}\frac{\theta_f}{Z_{\tau,\mathcal{D},\theta,\mathcal{E}}}
        \indicator[\text{match}(f',f)\not=\bot]}_{\text{Marginalize over which fragment produced $f,xs$}}\times\\&\prod_{n=1}^{|xs|}P_{\mathcal{D},\theta}(x_n|\tau_n,\mathcal{E})\prod_{e,\tau'\in \text{match}(f',f)}P_{\mathcal{D},\theta}(e|\tau',\mathcal{E})\\
      \\
      \text{match}(\lambda z.b,\lambda z.b')& = \text{match}(b,b')\\
      \text{match}(f\;x,f'\;x')& = \text{match}(f,f')\cup\text{match}(x,x')\\
      \text{match}(p,p)& = \varnothing \text{, $p$ a primitive or variable bound in fragment}\\
      \text{match}(v,p)& = \left\{v\mapsto p   \right\} \text{, $v$ a variable free in fragment, $p$ not containing free variables bound in fragment}\\
      \text{match}(e,e')& = \bot\text{, otherwise.}
      \\
      \\
      Z_{\tau,\mathcal{D},\theta,\mathcal{E}}& = \underbrace{\sum_{f:\tau_1\to\tau_2\to\cdots\to\tau\in \mathcal{D}\cup\mathcal{E}}\theta_f}_{\text{Normalizing constant for type $\tau$}}\\\\
      \text{parse}(f\;x)& = \left\{f',xs+[x] \;|\; f',xs\in \text{parse}(f) \right\}\cup\left\{f\;x \right\}\\
      \text{parse}(e)& = \left\{e,[] \right\} \text{, $e$ not an application}
    \end{align*}
  \end{minipage}
  \bottomrule
  \caption{Procedure for calculating likelihood of a program after a new fragment has been added to the DSL. For simplicity we omit typing context and reuse type variables to indicate unification, as is commonly done in e.g. Prolog.}\label{match}
  \end{figure}
